---
title: "STA6235 Week 5"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

## Tuesday, September 19

1. Show that the Gamma distribution is in the exponential family. 

## Thursday, September 21

Consider the Jackson Heart Study data from class. 

2. Download the data from Canvas and add to your `week-05-gamma` folder, then call it in here.

```{r}

```

3. Create a variable called *smoking* that combines *currentSmoker* (1 = current smoker, 0 = not current smoker) and *everSmoker* (1 = has smoked at least 200 cigarettes in their lifetime, 0 = has not smoked more than 200 cigarettes).

```{r}

```

4. Model HbA1c (*HbA1c*) as a function of age (*age*), waist circumference (cm; *waist*), hypertension medication use (*BPmeds*; 1 = takes blood pressure lowering medication, 0 = does not take blood pressure lowering drugs), the interaction between age and hypertension medication use, and the interaction between age and smoking status. Remember to report the final model

```{r}

```

5. Use the appropriate hypothesis test to determine if the interaction between age and smoking status is significant. Test at the $\alpha=0.05$ level. While you do not need to formally typeset the test results, you must state if it is significant and what statistical justification you have to make that statement.

```{r}

```

6. Use the appropriate hypothesis test to determine if the interaction between age and hypertension medication use is significant. Test at the $\alpha=0.05$ level. While you do not need to formally typeset the test results, you must state if it is significant and what statistical justification you have to make that statement.

```{r}

```

7. Construct a final model that includes all main effects and only *significant* interaction terms.

```{r}

```

8. Provide appropriate interpretations for the slopes in your final model. In the event that an interaction is in your model, please plug in *age* = 45 so that you can interpret the other slopes, skipping the interpretation for age.





9. Construct a graph to help you explain your final model to your collaborator. This graph should have *age* on the *x*-axis, *HbA1c* on the *y*-axis, with at least one line of your choosing.

```{r}

```

10. Did we need to use Gamma regression? Construct your final model under the normal distribution and assess necessary assumptions. Remember to draw a conclusion about the necessity of the Gamma distribution.

```{r}

```





